---
title: "Rip"
output: html_document
---

Project:  Riparian zone fires in the Sierra Nevadas

Question:  Do droughts change riparian zones from buffers (fire stoppers) to wicks (fire spreaders)? Do riparian management decisions have an effect?

Methods:
To determine wick vs buffer, I will look at fire severity classes for each fire. A way to test the effect of a riparian zone would be to see correlations between that zone and upland areas not directly adjacent. A buffer should show lesser severity than surrounding areas, and given ignition point, could slow spread of fire on side opposed to ignition start. However, depending on the severity and type, a fire may over throw the riparian zone.  A wick should show higher severity than surrounding areas, and have a positive correlation with areas in along the same slope but not adjacent. 

A way to connect this to drought is to look at streamflows in the area from the riparian zones.  Monthly departures from the long-term streamflow mean could be interpretted as drought.  A question: how long would an area need to have low streamflow to dessicate riparian zone vegetation? 

Obtain fire area/severity from MTBS.
Obtain riparian management from USDA Region 5: Sierra Nevadas
Obtain stream discharge from ... not sure.  Perhaps the same source as the recent lab

Riparian zone fire severity could be averaged for initial analysis.  Adjacent areas = same slope, within x distance?

It may be beneficial (at least as far as visualizing the thing) to limit the area by watershed.  
Or, as Erin suggested, convert the shapefile to raster format

```{r Data Manipulation}
install.packages("rgdal") #reading from shapefile
library(rgdal)
setwd("~/Desktop/RipShap")
ripshap <- readOGR(dsn = ".", layer = "Export_Output")

install.packages("rgeos") #converting coordinate system to lon/lat with WGS84
library(rgeos)
ripshapll <- spTransform(ripshap, CRS("+proj=longlat +datum=WGS84"))

#Found a function on rblogger to convert shapefile to raster, with conversion to lat lon?
shp2raster <- function(shp, mask.raster, label, value, transform = FALSE, proj.from = NA,
    proj.to = NA, map = TRUE) {
    require(raster, rgdal)
 
    # use transform==TRUE if the polygon is not in the same coordinate system as
    # the output raster, setting proj.from & proj.to to the appropriate
    # projections
    if (transform == TRUE) {
        proj4string(shp) <- proj.from
        shp <- spTransform(shp, proj.to)
    }
 
    # convert the shapefile to a raster based on a standardised background
    # raster
    r <- rasterize(shp, mask.raster)
    # set the cells associated with the shapfile to the specified value
    r[!is.na(r)] <- value
    # merge the new raster with the mask raster and export to the working
    # directory as a tif file
    r <- mask(merge(r, mask.raster), mask.raster, filename = label, format = "GTiff",
        overwrite = T)
 
    # plot map of new raster
    if (map == TRUE) {
        plot(r, main = label, axes = F, box = F)
    }
 
    names(r) <- label
    return(r)
}

sn_mask <- 

library(ggplot2) #converting to a format that ggplot will understand
rip.points <- fortify(ripshapll)
rip.broom <- tidy(ripshapll)
summary(rip.points) #find the mean lat lon to use for mapImage

library(RColorBrewer) #terrain colors for map
colors <- brewer.pal(9, "BuGn")

library(ggmap) #making map of Area
mapImage <- get_map(location = c(lon = -119.4, lat = 38.1),
  color = "color",
  source = "osm",
  # maptype = "terrain",
  zoom = 9)

ggmap(mapImage) +geom_polygon(aes(x = long,
      y = lat,
      group = group),
      data = rip.points,
    color = colors[9],
    fill = colors[6],
    alpha = 0.5) +
labs(x = "Longitude",
  y = "Latitude")

ggplot(data = rip.points[1:100000,], aes(x = long, y = lat, group = group)) + geom_polygon() #So 5 million data points are a lot of data points.   Lets subset by a region at first, then maybe do the entire sierras.

library(ggplot2)
rip.points <- fortify(ripshapll)

```


```{r Burn mosiacs}
BurSev_14 <- readGDAL("~Desktop/RipShap/mtbs_conus_1984_20160401/mtbs_CONUS_dt_1984_20160401.tif")
file.exists("~/Desktop/RipShap/mtbs_conus_1984_20160401/mtbs_CONUS_dt_1984_20160401.tif")
